Smart quotes, em dashes, and en dashes

### 2021-09-28 text/20/smart-quotes.Rmd
Dropped Reccomended and Blog post from titles.

---
title: "Blog post: Smart quotes, em dashes, and en dashes"
author: "Steve Simon"
source: "New"
date: "2020-03-02"
category: Blog post
tags: Data management
output: html_document
---

>>>>

---
title: "Smart quotes, em dashes, and en dashes"
author: "Steve Simon"
source: "New"
date: "2020-03-02"
categories:
- Blog post
tags:
- Data management
output: html_document
---
